### 2014-10-29 contract-language.tex
edits

\name contracts are constraints over axiomatic definitions of program
executions.Fig.~\ref{sem:contracts} summarizes artifacts relevant to
define an axiomatic execution. We formalize an axiomatic execution as
a tuple $\Exec$, where $\EffSoup$, called the \emph{effect soup}, is
the set of all effects generated during the program execution, and
$\visZ,\soZ, \sameobjZ \subseteq \EffSoup \times \EffSoup$ are
\emph{visibility}, \emph{session order}, and \emph{same object}
relations, respectively, witnessed over generated effects at run-time.

>>>>

\name contracts are constraints over axiomatic definitions of program
executions.Fig.~\ref{sem:contracts} summarizes artifacts relevant to
define an axiomatic execution. We formalize an axiomatic execution as
a tuple $\Exec$, where $\EffSoup$, called the \emph{effect soup}, is
the set of all effects generated during the program execution, and
$\visZ,\soZ,\sameobjZ \subseteq \EffSoup \times \EffSoup$ are
\emph{visibility}, \emph{session order}, and \emph{same object}
relations, respectively, witnessed over generated effects at run-time.

### 2014-10-29 implementation.tex
edits

In this section, we describe the instantiation of \name on top of off-the-shelf
eventually consistent distributed store Cassandra. We begin with a description
of the programming interface.

The programmer simply pairs up the operation implementation with the
corresponding contract to complete the RDT implementation. The contracts are
statically checked, and mapped to the corresponding store consistency level.
The store is exposed as a collection key-indexed, object-valued tables, where
each table holds objects of the same type. The transaction language operates
over this view, and has primitives to invoke an operation on an object, and
invoke a transaction on a sequence of operation invocations. The transaction
contract is also statically checked and classified.

>>>>

In this section, we describe the instantiation of \name on top of off-the-shelf
eventually consistent distributed store Cassandra. In particular, we focus on
the challenges in efficiently realizing \name programming model.
